quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-09 paper-quollr.Rmd
Updated Figure 9

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "300px", height = "300px")

@@

lndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        nldr_plt, htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

>>>>

detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 0.5, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "300px", height = "300px")

@@

lndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 350px;
    width: 300px;",
        nldr_plt, htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

### 2025-12-09 paper-quollr.tex
Updated Figure 9

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "300px", height = "300px")
\end{verbatim}

\begin{verbatim}
lndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
        nldr_plt, htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)

>>>>

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 0.5, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "300px", height = "300px")
\end{verbatim}

\begin{verbatim}
lndet_link <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;
    height: 350px;
    width: 300px;",
        nldr_plt, htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
)
